Demo arXiv template

### 2023-02-13 paper/paper.qmd
conclusion

## Calculating indexes on raster data

<!-- Raster data is common data format for delivering large satellite spatio-temporal data.  -->

<!-- Issue 1: variables may be collected at different spatial and temporal extent/ scale, different resolutions and granularities.  -->

<!-- cleaning these variables involves spatial and temporal processing.  -->

<!-- Issue 2: what the data the step is operated on?? -->

<!-- When calculating on raster data, it is confusing on what data the operation is on. Is the operation operated per pixel or across regions, is the operation operated across all the time point, across year, across month etc.  -->

<!-- While it may be clear to researchers themselves, but can be confusing for others who read the analysis for the first time.  -->

<!-- The data structure should be made explicit at each operation on the spatio-temporal raster data, in terms of inputs and outputs. -->

<!-- The raster examples  -->

>>>>

# Conclusion

The paper presents a data pipeline with nine modules for constructing and analysing indexes. The pipeline increases transparency in the practice for index analysts to experiment with different index design and parameter choices to better design and apply their indexes. The significance of this work is its ability to provide a universal framework for index construction, which can be applied across different domains.

Examples have been given in the drought indexes and human development index to demonstrate computing of indexes with different parameters combinations and how alternative index design can provide insights to understand distinctive country characteristics that could sometimes be overlooked. The accompanied package, PACKAGE, is not meant to provide comprehensive implementation for all indexes across all domains. Instead, it demonstrates implementing individual pipeline steps that are versatile to multiple indexes and composing new indexes from existing steps. Domain experts are welcomed to adopt the pipeline approach to develop specialised packages for specific-domains indexes.

### 2023-02-13 paper/paper.tex
conclusion

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{calculating-indexes-on-raster-data}{%
\subsection{Calculating indexes on raster
data}\label{calculating-indexes-on-raster-data}}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, frame hidden, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

The paper presents a data pipeline with nine modules for constructing
and analysing indexes. The pipeline increases transparency in the
practice for index analysts to experiment with different index design
and parameter choices to better design and apply their indexes. The
significance of this work is its ability to provide a universal
framework for index construction, which can be applied across different
domains.

Examples have been given in the drought indexes and human development
index to demonstrate computing of indexes with different parameters
combinations and how alternative index design can provide insights to
understand distinctive country characteristics that could sometimes be
overlooked. The accompanied package, PACKAGE, is not meant to provide
comprehensive implementation for all indexes across all domains.
Instead, it demonstrates implementing individual pipeline steps that are
versatile to multiple indexes and composing new indexes from existing
steps. Domain experts are welcomed to adopt the pipeline approach to
develop specialised packages for specific-domains indexes.
